\section{Requirements}
In order to be able to conclude upon the success of the project, a fixed set of requirements must be formulated.
These requirements will serve as a guideline in the conclusion of the report and as markers throughout the project. 
To formally specify the requirements, the MoSCoW analysis model will be utilized. 
The MoSCoW model specifies which requirements \textbf{M}ust, \textbf{S}hould, \textbf{C}ould, and \textbf{W}on't be fulfilled to deem the project successful.\\
Throughout this analysis, the term \textit{target} will refer to respectively a small target, eg{.} a ball with a diameter of approximately 10 centimeters or a large target, eg{.} an inflated balloon.
The requirements of the system are based upon the results of the points examined in the rest of problem analysis.

\textbf{Must have}
\begin{itemize}
\item ability to recognize and track a moving target in front of the device
\item ability to follow a small target being dropped from 2 meters height at a distance of 3 to 4 meters away from the device, with a laser
\item move fast enough to keep the laser on a moving target in real time
\item ability to move the laser at least 60 degrees in both horizontal and vertical directions from the origin.
\item ability to predict the next location of the object moving solely along the horizontal axis with a constant speed
\item enough structural stability to be able to move without breaking
\end{itemize}

\textbf{Should have}
\begin{itemize}
\item ability to hit a larger moving target in the air at a low speed at a distance of 3 meters
\item ability to hit a small moving target in the air at a low speed at a distance of 1 to 3 meters
\item ability to predict the next location of the object moving along a non-linear path, eg{.} a target that continuously moves back and forth on the vertical axis while moving linearly on the horizontal axis.
\end{itemize}

\textbf{Could have}
\begin{itemize}
\item ability to calculate the distance to the target object
\item calculate the angle and power necessary to hit the target with a projectile
\end{itemize}

\textbf{Won't have at this time}
\begin{itemize}
\item ability to actually take down targets
\item ability to differentiate between the type of object that is being observed
\end{itemize}

By fulfilling the requirements specified in the \textit{must have} section, the device will be able to track a target with a rather predictable movement pattern and use the attached laser to indicate the tracking. 
With the \textit{should have} requirements the functionality of the device is extended to track more advanced movement patterns, which in a real life scenario could be drones or birds in the air while still using the laser to indicate the tracking.
If the \textit{could have} requirements are fulfilled the device will be able to calculate the distance to the observed target, calculate angle and power required to hit the target and fire a ballistic projectile at it.
Finally, the \textit{won't have} requirements are deemed outside the scope of the current project and focus on the future application of the device, which would require more efficient projectiles in order to take down the observed target and being able to differentiate between whether the object is a threat or not.